---
title: "logistic_mod"
author: "Amanda Elert"
date: "4/13/2020"
output: md_document
---
```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(lubridate)
two_points <- read_csv("two_point_attempts.csv") %>% 
  mutate(play_type = as.factor(play_type),
         weather_detail = as.factor(weather_detail))
# str(two_points)
```
# Logistic Regression
We created a logistic regression model to determine what variables were significant in predicting the success probability of a two-point conversion. Because we are testing our thesis that a run play is a more successful option than a pass play, we included numerous variables that quantify the team's success with running the ball in the game up until the two-point conversion attempt.
<br>
```{r}
glm_twopt <- glm(two_point_conv_result ~ prop_runs_greater_than_2_yards + prop_passes_greater_than_2_yards + total_pass_yards + total_run_yards + num_runs + num_passes + avg_yds_per_play + completion_percentage + play_type + score_differential + avg_yards_per_run + avg_yards_per_pass, family = binomial(link= "logit"), data=two_points, na.action = na.exclude)

summary(glm_twopt)
```

```{r include=FALSE}
quantile(two_points$prop_runs_greater_than_2_yards, na.rm = T)
```



