---
title: "logistic_mod"
author: "Amanda Elert"
date: "4/13/2020"
output: md_document
---
```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(lubridate)
library(MASS)
two_points <- read_csv("two_point_attempts.csv") %>% 
  mutate(play_type = as.factor(play_type),
         weather_detail = as.factor(weather_detail)) %>% 
  drop_na(third_down_conv_percentage)
```
# Modeling
We tried a couple statistical methods to predict whether a two-point conversion would be successful or not. We shared our work and results here.
<br>
<br>

## Model 1: Logistic Regression
We created a logistic regression model to determine what variables were significant in predicting the success probability of a two-point conversion. Because we are testing our thesis that a run play is a more successful option than a pass play, we included numerous variables that quantify the team's success with running the ball in the game up until the two-point conversion attempt.
<br>
```{r}
glm_twopt <- glm(two_point_conv_result ~ prop_runs_greater_than_2_yards + prop_passes_greater_than_2_yards + total_pass_yards + total_run_yards + num_runs + num_passes + avg_yds_per_play + completion_percentage + play_type + score_differential + avg_yards_per_run + avg_yards_per_pass + score_differential + game_seconds_remaining + third_down_conv_percentage, family = binomial(link= "logit"), data = two_points, na.action = na.exclude)
```
<br>
We then used the stepAIC function to select the best predictors to use in our logistic regression model. This is the model that the stepAIC function selected. 
```{r include=FALSE}
aic_glm <- stepAIC(glm_twopt)
```

```{r}
summary(aic_glm)
```

```{r include=FALSE}
quantile(two_points$prop_runs_greater_than_2_yards, na.rm = T)
```
<br>

### Model 1: Data Vis
We use a binomial modeling technique to graph relationship between probability of successful two-point conversion and the predictors.
<br>
<br>
**The probability of two point conversion success increases as the number of total passing yards increases.**
```{r}
ggplot(two_points, aes(x = total_pass_yards, y = two_point_conv_result)) + 
  geom_point() + 
  stat_smooth(method = "glm", method.args = list(family="binomial"), se = FALSE) +
  labs(x = "Total Passing Yards (Up Until to the 2PT Conv. Attempt)", y = "Probability of 2PT Conv. Success")
```
<br>
<br>
<br>
<br>
**The probability of two point conversion success descreases as the number of passes thrown by the possession team increases.**
```{r}
ggplot(two_points, aes(x = num_passes, y = two_point_conv_result)) + 
  geom_point() + 
  stat_smooth(method = "glm", method.args = list(family="binomial"), se = FALSE) +
  labs(x = "Number of Pass Attempts (Up Until to the 2PT Conv. Attempt)", y = "Probability of 2PT Conv. Success")
```
<br>
<br>
<br>
<br>
**The probability of two point conversion success descreases when there is more time remaining in the game.**
```{r}
ggplot(two_points, aes(x = game_seconds_remaining/60, y = two_point_conv_result)) + 
  geom_point() + 
  stat_smooth(method = "glm", method.args = list(family="binomial"), se = FALSE) +
  labs(x = "Game Minutes Remaining (At the 2PT Conv. Attempt)", y = "Probability of 2PT Conv. Success")
```


