---
title: "logistic_mod"
author: "Amanda Elert"
date: "4/13/2020"
output: md_document
---
```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(lubridate)
library(caret)
library(factoextra)
library(e1071)
#library(MASS)

two_points <- read_csv("two_point_attempts.csv") %>% 
  mutate(play_type = as.factor(play_type),
         weather_detail = as.factor(weather_detail)) %>% 
  drop_na(third_down_conv_percentage)
```
# Methods and Results
We tried a couple statistical methods to predict whether a two-point conversion would be successful or not. We shared our work and results here.
<br>
<br>

## Model 1: Logistic Regression
We created a logistic regression model to determine what variables were significant in predicting the success probability of a two-point conversion. Because we are testing our thesis that a run play is a more successful option than a pass play, we included numerous variables that quantify the team's success with running the ball in the game up until the two-point conversion attempt.
<br>
```{r}
glm_twopt <- glm(two_point_conv_result ~ prop_runs_greater_than_2_yards + prop_passes_greater_than_2_yards + total_pass_yards + total_run_yards + num_runs + num_passes + avg_yds_per_play + completion_percentage + play_type + score_differential + avg_yards_per_run + avg_yards_per_pass + score_differential + game_seconds_remaining + third_down_conv_percentage, family = binomial(link= "logit"), data = two_points, na.action = na.exclude)
```
<br>
We then used the stepAIC function to select the best predictors to use in our logistic regression model. This is the model that the stepAIC function selected. 
```{r include=FALSE}
# aic_glm <- stepAIC(glm_twopt)
# The MASS package messes up the Select dplyr function, so we are commenting out the stepAIC function and just setting the function to what the stepAIC function gave us.
aic_glm <- glm(two_point_conv_result ~ total_pass_yards + num_passes + play_type + game_seconds_remaining, family = binomial(link= "logit"), data = two_points, na.action = na.exclude)
```

```{r}
summary(aic_glm)
```

```{r include=FALSE}
quantile(two_points$prop_runs_greater_than_2_yards, na.rm = T)
```
<br>

### Model 1: Data Visualization
We use a binomial modeling technique to graph relationship between probability of successful two-point conversion and the predictors.
<br>
<br>
**The probability of two point conversion success increases as the number of total passing yards increases.**
```{r}
ggplot(two_points, aes(x = total_pass_yards, y = two_point_conv_result)) + 
  geom_point() + 
  stat_smooth(method = "glm", method.args = list(family="binomial"), se = FALSE) +
  labs(x = "Total Passing Yards (Up Until to the 2PT Conv. Attempt)", y = "Probability of 2PT Conv. Success")
```
<br>
<br>
<br>
<br>
**The probability of two point conversion success descreases as the number of passes thrown by the possession team increases.**
```{r}
ggplot(two_points, aes(x = num_passes, y = two_point_conv_result)) + 
  geom_point() + 
  stat_smooth(method = "glm", method.args = list(family="binomial"), se = FALSE) +
  labs(x = "Number of Pass Attempts (Up Until to the 2PT Conv. Attempt)", y = "Probability of 2PT Conv. Success")
```
<br>
<br>
<br>
<br>
**The probability of two point conversion success descreases when there is more time remaining in the game.**
```{r}
ggplot(two_points, aes(x = game_seconds_remaining/60, y = two_point_conv_result)) + 
  geom_point() + 
  stat_smooth(method = "glm", method.args = list(family="binomial"), se = FALSE) +
  labs(x = "Game Minutes Remaining (At the 2PT Conv. Attempt)", y = "Probability of 2PT Conv. Success")
```
<br>
<br>
<br>
<br>

## Model 2: Support Vector Machine
MIKE EDIT HERE
<br>
```{r include=FALSE}
svm_df <- two_points %>%
  select(two_point_conv_result,
         score_differential,
         score_differential_post,
         completion_percentage,
         qtr,
         game_seconds_remaining,
         total_yards_gained,
         num_runs,
         num_passes,play_num,
         num_runs_greater_than_2yds,
         num_runs_greater_than_2yds,
         prop_runs_greater_than_2_yards,
         prop_passes_greater_than_2_yards,
         avg_yards_per_run,
         avg_yards_per_pass)

svm_df <- drop_na(svm_df)

variables_lowCorrelation1 <- svm_df %>%
  select(two_point_conv_result,
         score_differential,
         total_yards_gained,
         prop_passes_greater_than_2_yards,
         completion_percentage,
         prop_runs_greater_than_2_yards,
         game_seconds_remaining)
```

```{r}
accuracyList = 0
for (i in (1:100)){
  variables_lowCorrelation <- na.omit(variables_lowCorrelation1)
  n <- nrow(variables_lowCorrelation)
  ntrain <- round(n*.9)
  svm_plays <- sample(n, ntrain)
  train_plays <- variables_lowCorrelation[svm_plays,]
  test_plays <- variables_lowCorrelation[-svm_plays,]
  
  model <- svm(formula = two_point_conv_result ~ ., data = train_plays, type = 'C-classification', kernel = 'polynomial')
  
  radialPredict = predict(model, test_plays)
  confusion <- confusionMatrix(table(test_plays$two_point_conv_result, radialPredict))
  accuracyList <- accuracyList + confusion$overall[["Accuracy"]]
}

accuracyList/100
```
<br>
<br>

### Model 2: Data Visualization
ARE WE DOING THIS?
<br>
<br>
<br>
<br>

## Model 3: Principle Component Analysis
MIKE ADD HERE
<br>
```{r}
run.pr <- prcomp(svm_df[1:15], center = TRUE, scale = TRUE)
```
<br>
<br>

### Model 3: Data Visualization
```{r}
fviz_pca_ind(run.pr, geom.ind = "point", pointshape = 21, 
             pointsize = 2, 
             fill.ind = as.factor(svm_df$two_point_conv_result), 
             col.ind = "black", 
             palette = "jco", 
             addEllipses = TRUE,
             label = "var",
             col.var = "black",
             repel = TRUE,
             legend.title = "2-Point Conversion Result") +
  ggtitle("2D PCA-plot from 15 feature dataset") +
  theme(plot.title = element_text(hjust = 0.5))
```
